workshop

### 2022-09-13 scripts/workshop.Rmd
update text
update with fig 2
add text about next steps

@@

The manhattan distance is equivalent to bray-curtis distance

>>>>

![motivating figure](https://dcsuh.github.io/rana-competence/figures/fig_2.png)

@@

sometimes similar and sometimes not

## next step

do PCA after Hellinger transformation of data. PCA has the double zero problem but Hellinger distance avoids that problem and avoids overweighting of abundance data by turning absolute species abundances into relative abundances. more info [here](https://davidzeleny.net/blog/2022/03/17/euclidean-distance-is-sensitive-to-double-zero-problem-while-hellinger-is-not-visualization/)
